Assessing MCR Discussion Usefulness using Semantic Similarity

### 2014-09-17 sections/approach.tex
Add references and fit page length

\begin{figure}[!t]
\centering
\includegraphics[scale=0.34, trim = 50 90 0 30, clip=true]{overview2}
\caption{An overview of classification of comment usefulness using semantic similarity}
\label{fig:overview}
\end{figure}

@@

The model is a form of \emph{supervised classification} % \cite{wiki:supervised}
where a training set is used to empirically derive similarity and dissimilarity thresholds that optimize meaningful likelihoods e.g. likelihood that a comment is useful given its similarity is greater than some threshold value.    
The training data is a small set of randomly-selected pairs of comments and the corresponding commit messages.
These comments are manually assessed for usefulness.
%Each comment is assessed by three different people independently.
%For each \texttt{YES} vote, a single point is given to that comment.
%This means that a comment will receive a score of 0, 1, 2, or 3.
For statistical purposes, at least 30 useful and 30 useless comments must be collected.
The similarity and dissimilarity metrics are then computed for the training data set.
These are used to estimate the similarity and dissimilarity thresholds $S_T$ and $D_T$ that best discriminate useful comments and $S'_T$ and $D'_T$ from useless comments. 
%Other likelihood functions could be used depending on precision, recall, or risk goals.
We find these thresholds by selecting $s_t,d_t$ values that maximize the F-measure \footnote{\url{http://en.wikipedia.org/w/index.php?title=F1_score&oldid=608940880}},
which is a performance measure for a binary classification that compromises trade-offs in accuracy of classification (precision) and coverage of classification (recall).
In this study, we used the F$_1$-measure, which equally prioritizes precision and recall.
Different weighting can be used by different F$_\beta$ measures depending on error tolerance for precision and recall.

>>>>

\begin{figure}[!t]
\centering
\includegraphics[scale=0.32, trim = 50 90 0 30, clip=true]{overview2}
\caption{An overview of classification of comment usefulness using semantic similarity}
\label{fig:overview}
\end{figure}

@@

The model is a form of \emph{supervised classification} % \cite{wiki:supervised}
where a training set is used to empirically derive similarity and dissimilarity thresholds that optimize meaningful likelihoods e.g. likelihood that a comment is useful given its similarity is greater than some threshold value.    
The training data is a small set of randomly-selected pairs of comments and the corresponding commit messages.
These comments are manually assessed for usefulness.
%Each comment is assessed by three different people independently.
%For each \texttt{YES} vote, a single point is given to that comment.
%This means that a comment will receive a score of 0, 1, 2, or 3.
For statistical purposes, at least 30 useful and 30 useless comments must be collected\cite{Hogg2005}.
The similarity and dissimilarity metrics are then computed for the training data set.
These are used to estimate the similarity and dissimilarity thresholds $S_T$ and $D_T$ that best discriminate useful comments and $S'_T$ and $D'_T$ from useless comments. 
%Other likelihood functions could be used depending on precision, recall, or risk goals.
We find these thresholds by selecting $s_t,d_t$ values that maximize the F-measure \cite{Prasetyo2012,Gottipati2011}
which is a performance measure for a binary classification that compromises trade-offs in accuracy of classification (precision) and coverage of classification (recall).
%In this study, we used the F$_1$-measure, which equally prioritizes precision and recall.
%Different weighting can be used by different F$_\beta$ measures depending on error tolerance for precision and recall.

### 2014-09-17 sections/background.tex
edit stuff a lot
Add references and fit page length

Ultimately our aim is to understand the impact of useful and useless comments on code quality. Specifically, what degree of useful comments are needed to effect positive impact on quality. Study of this necessitates ascertaining, with high confidence, the usefulness of a large number of comments. This  had proven difficult to accomplish manually, so here we investigate the pragmatics of using semantic similarity to assist with this task.

\begin{figure}[!t]
\centering
\includegraphics[scale=0.4, trim= 100 250 0 0, clip=true]{comment_examples}
\caption{Examples of comment in code reviews of Qt project.}
\label{fig:example}
\end{figure}

>>>>

Ultimately, our aim is to understand the impact of useful and useless comments on code quality. Specifically, what degree of useful comments are needed to effect positive impact on quality. Study of this necessitates ascertaining, with high confidence, the usefulness of a large number of comments. This  had proven difficult to accomplish manually, so here we investigate the pragmatics of using semantic similarity to assist with this task.

\begin{figure}[!t]
\centering
\includegraphics[scale=0.33, trim= 100 250 0 0, clip=true]{comment_examples}
\caption{Examples of comment in code reviews of Qt project.}
\label{fig:example}
\end{figure}

### 2014-09-17 sections/introduction.tex
very minor fixes
Add references and fit page length

\section{Introduction}
Software code review is a well-established software quality management practice.
Fundamentally, the intent is to identify defects early and encourage quality development policy and practices (such as adherence to coding standards and improving code readability).
Traditionally, code reviews were a highly structured activity, but nowadays, less formal and lightweight code reviews such as Modern Code Review (MCR)\cite{Bacchelli2013a} are commonly used within both industry and OSS projects. 
One reason for this is that with MCR, unlike formal inspections \cite{Fagan:1976:DCI:1661010.1661012}, in-person meetings are not required.
Reviewers can find problems in proposed changes and hold discussions on them by adding comments through a code review tool or a mailing list.
Developers then improve the changes in response to these comments and re-submit for review until the changes are approved.  
%Fig. \ref{fig:process} illustrates a typical MCR process. 
The popularity of MCR and readily available data have made it an attractive research area.  
In particular, because performance of code review has a clear relationship to the quality of the software, many studies have investigated the factors that influence MCR\cite{Baysal2001,Mcintosh,Beller,Hamasaki2013} effectiveness.
However, little research exists investigating \emph{how} review discussion for a proposed change impacts software quality.
Given that most proposed changes are triggered from reviewer comments \cite{Beller}, 
it's possible that comments can either positively contribute to the proposed changes (i.e. are ``\emph{useful}''), or be a discussion which contributes little directly to the proposed changes (i.e. relatively ``\emph{useless}''). 
Since MCR does not require strict guidelines, checklists, or formal processes, some reviewers tend to focus on trivial issues (e.g. coding styles), leaving deeper and possibly more quality-important issues undiscussed \cite{Bacchelli2013a}.
%This is a concern because a high-degree of useless comments not only fails to contribute to improving quality, but also degrades the cost-effectiveness and perceived utility of MCR.
This is a concern because a low-degree of useful comments may degrade the overall effectiveness and perceived utility of MCR.

Prior research has focused primarily on the relationship between number of comments and quality.
To the best of our knowledge, the connection between degree of useful and useless comments and quality has not been studied.
One reason for this may be that to assess the impact of discussion in MCR, an effort-intensive manual classification is required as in the study of Beller et. al. \cite{Beller}.
So while the data may be easy to access, MCR can produce a massive amounts of change requests and comments\cite{Balachandran2013,Thongtanunam2014} and it is painstaking and time consuming to manually assess their usefulness.
Moreover, given that comments in MCR are unstructured natural text, open to subjective judgment, contain tacit understanding, and possible misinterpretation, assessment errors are inevitable.

@@

\begin{figure}[!t]
\centering
\includegraphics[scale=0.35, trim= 100 110 50 80, clip=true]{review_process}
\caption{An simplified version of MCR Process based on Gerrit system}
\label{fig:process}
\end{figure}

>>>>

\section{Introduction}
Software code review is a well-established software quality management practice.
Fundamentally, the intent is to identify defects early and encourage quality development policy and practices (such as adherence to coding standards and improving code readability).
Traditionally, code reviews were a highly structured activity, but nowadays, less formal and lightweight code reviews such as Modern Code Review (MCR)\cite{Bacchelli2013a} are commonly used within both industry and OSS projects. 
One reason for this is that with MCR, unlike formal inspections \cite{Beller}, in-person meetings are not required.
Reviewers can find problems in proposed changes and hold discussions on them by adding comments through a code review tool or a mailing list.
Developers then improve the changes in response to these comments and re-submit for review until the changes are approved.  
%Fig. \ref{fig:process} illustrates a typical MCR process. 
The popularity of MCR and readily available data have made it an attractive research area.  
In particular, because performance of code review has a clear relationship to the quality of the software, many studies have investigated the factors that influence MCR\cite{Baysal2001,Mcintosh,Beller,Hamasaki2013} effectiveness.
However, little research exists investigating \emph{how} review discussion for a proposed change impacts software quality.
Given that most proposed changes are triggered from reviewer comments \cite{Beller}, 
it's possible that comments can either positively contribute to the proposed changes (i.e. are ``\emph{useful}''), or be a discussion which contributes little directly to the proposed changes (i.e. relatively ``\emph{useless}''). 
Since MCR does not require strict guidelines, checklists, or formal processes, some reviewers tend to focus on trivial issues (e.g. coding styles), leaving deeper and possibly more quality-important issues undiscussed \cite{Bacchelli2013a}.
%This is a concern because a high-degree of useless comments not only fails to contribute to improving quality, but also degrades the cost-effectiveness and perceived utility of MCR.
This is a concern because a low-degree of useful comments may degrade the overall effectiveness \cite{Prasetyo2012,Gottipati2011} and perceived utility of MCR.

Prior research has focused primarily on the relationship between number of comments and quality.
To the best of our knowledge, the connection between degree of useful and useless comments and quality has not been studied.
One reason for this may be that to assess the impact of discussion in MCR, an effort-intensive manual classification is required as in the study of Beller et. al. \cite{Beller}.
So while the data may be easy to access, MCR can produce a massive amounts of change requests and comments\cite{Thongtanunam2014} and it is painstaking and time consuming to manually assess their usefulness.
Moreover, given that comments in MCR are unstructured natural text, open to subjective judgment, contain tacit understanding, and possible misinterpretation, assessment errors are inevitable.

@@

\begin{figure}[!t]
\centering
\includegraphics[scale=0.28, trim= 100 110 50 80, clip=true]{review_process}
\caption{A simplified version of MCR Process based on Gerrit system}
\label{fig:process}
\end{figure}
